{RandomRationalPoints} package for \emph{Macaulay2}

### 2021-04-20 FastLinAlg/M2/ChangesMade_ResponseToReviewers.txt

However, doing a saturation with respect to every variable (even separately) seems to make this function quite a bit slower.  We are tempted to saturate with respect to a (random) variable, then use a try command to see if that yields a good result, and if it crashed try saturating with respect to a different (random) variable.  However, we

New documentation and examples have been provided.

All the strategies now make use of the dimViaBezout to compute the dimension of the given ideal, if the codimension is not already known. In case, that it is known, it should be specified along with the call of randomPoints.

ProjectionAttempts has been set to 0 in the Default Strategy now for reasons discussed.

-------------------------------

We also provide some examples demonstrating performance in some somewhat larger examples.

-------------------------
----Large Example #1-----
-------------------------

-------------------------
----Large Example #3-----
-------------------------

Here is an example (coming out of a jacobian computation) where the rational points tend to be saturated away, which causes the MultiplicationTable strategy to fail (at least based on our understanding).

In this example, the primary speed limitation still appears to be the dimension computation.

T2 = ZZ/101[x1,x2,x3,x4,x5,x6,x7, Z];
J2 = ideal(x5*x6-x4*x7,x1*x6-x2*x7,x5^2-x1*x7,x4*x5-x2*x7,x4^2-x2*x6,x1*x4-x2*x5,x2*x3^3*x5+3*x2*x3^2*x7*Z+8*x2^2*x5*Z^2+3*x3*
      x4*x7*Z^2-8*x4*x7*Z^3+x6*x7*Z^3,x1*x3^3*x5+3*x1*x3^2*x7*Z+8*x1*x2*x5*Z^2+3*x3*x5*x7*Z^2-8*x5*x7*Z^3+x7^2*Z^3,x2*x3^3*x4+3*
      x2*x3^2*x6*Z+8*x2^2*x4*Z^2+3*x3*x4*x6*Z^2-8*x4*x6*Z^3+x6^2*Z^3,x2^2*x3^3+3*x2*x3^2*x4*Z+8*x2^3*Z^2+3*x2*x3*x6*Z^2-8*x2*x6*
      Z^3+x4*x6*Z^3,x1*x2*x3^3+3*x2*x3^2*x5*Z+8*x1*x2^2*Z^2+3*x2*x3*x7*Z^2-8*x2*x7*Z^3+x4*x7*Z^3,x1^2*x3^3+3*x1*x3^2*x5*Z+8*x1^2
      *x2*Z^2+3*x1*x3*x7*Z^2-8*x1*x7*Z^3+x5*x7*Z^3,x1*x2^2*x4-x2^3*x5,-x1^2*x3^3*x5^2-6*x1*x3^2*x5^3*Z-6*x3*x5^4*Z^2-3*x1*x3*x5^
      2*x7*Z^2+16*x5^4*Z^3+8*x1*x5^2*x7*Z^3-4*x5^3*x7*Z^3,-x2^2*x3^3*x4^2-6*x2*x3^2*x4^3*Z-8*x2^3*x4^2*Z^2-6*x3*x4^4*Z^2-3*x2*x3
      *x4^2*x6*Z^2+16*x4^4*Z^3+8*x2*x4^2*x6*Z^3-4*x4^3*x6*Z^3,-2*x3^3*x5^2*x7^2-x1*x3^3*x7^3-6*x3^2*x5*x7^3*Z-8*x1*x5^2*x6*x7*Z^
      2-8*x1*x4*x5*x7^2*Z^2-16*x2*x5^2*x7^2*Z^2-8*x1*x2*x7^3*Z^2-3*x3*x7^4*Z^2+8*x7^4*Z^3,-8*x1^5,-x1^2*x3^3*x5^2+x1^3*x3^3*x7-6
      *x1*x3^2*x5^3*Z+6*x1^2*x3^2*x5*x7*Z+8*x1^3*x4*x5*Z^2-16*x1^2*x2*x5^2*Z^2-6*x3*x5^4*Z^2+8*x1^3*x2*x7*Z^2+3*x1*x3*x5^2*x7*Z^
      2+3*x1^2*x3*x7^2*Z^2+16*x5^4*Z^3-8*x1*x5^2*x7*Z^3-4*x5^3*x7*Z^3-8*x1^2*x7^2*Z^3+4*x1*x5*x7^2*Z^3,-x1^2*x5^2+x1^3*x7,-6*x1^
      2*x2*x3^5*x5*x7-30*x1*x2*x3^4*x5^2*x7*Z-48*x1^2*x2^2*x3^2*x5*x7*Z^2-36*x2*x3^3*x5^3*x7*Z^2-24*x1*x2*x3^3*x5*x7^2*Z^2+5*x1*
      x2^2*x3*x5^2*x7*Z^3+48*x1*x2*x3^2*x5*x7^2*Z^3+47*x2*x3^2*x5^2*x7^2*Z^3-3*x1*x2*x3^2*x7^3*Z^3-48*x1*x2^2*x5*x7^2*Z^4-5*x2*
      x3*x5^2*x7^2*Z^4-24*x2*x3*x5*x7^3*Z^4+48*x2*x5*x7^3*Z^5-3*x2*x7^4*Z^5,18*x1^2*x2^3*x3^6+24*x1^2*x2^3*x3^5*Z+24*x1^2*x2^2*
      x3^5*x4*Z+9*x1*x2^3*x3^5*x5*Z+29*x1^2*x2^4*x3^3*Z^2+29*x1^2*x2^2*x3^4*x4*Z^2+19*x1*x2^3*x3^4*x5*Z^2-6*x1*x2^2*x3^4*x4*x5*Z
      ^2-9*x2^3*x3^4*x5^2*Z^2+18*x1*x2^3*x3^4*x7*Z^2-10*x1^2*x2^4*x3^2*Z^3-24*x1^2*x2^3*x3^2*x4*Z^3-43*x1*x2^4*x3^2*x5*Z^3-45*x1
      *x2*x3^3*x4^2*x5*Z^3-18*x2^2*x3^3*x4*x5^2*Z^3+43*x1^2*x2^2*x3^3*x6*Z^3+9*x1*x2^2*x3^3*x5*x6*Z^3+24*x1*x2^3*x3^3*x7*Z^3+24*
      x1*x2^2*x3^3*x4*x7*Z^3-20*x1*x2^4*x3*x5*Z^4-48*x1*x2^3*x3*x4*x5*Z^4-39*x1*x2*x3^2*x4^2*x5*Z^4-15*x2*x3^2*x4^2*x5^2*Z^4+10*
      x1^2*x2^2*x3^2*x6*Z^4+19*x1*x2^2*x3^2*x5*x6*Z^4-18*x1*x2*x3^2*x4*x5*x6*Z^4+3*x2^2*x3^2*x5^2*x6*Z^4+6*x1^2*x2*x3^2*x6^2*Z^4
      +29*x1*x2^4*x3*x7*Z^4+29*x1*x2^2*x3^2*x4*x7*Z^4+20*x1*x2*x3*x4^2*x5*Z^5+48*x2*x3*x4^2*x5^2*Z^5+48*x1*x2*x3*x4*x5*x6*Z^5+9*
      x1*x3*x4^2*x5*x6*Z^5-48*x2^2*x3*x5^2*x6*Z^5-6*x2*x3*x4*x5^2*x6*Z^5-6*x1*x2*x3*x5*x6^2*Z^5-10*x1*x2^4*x7*Z^5-24*x1*x2^3*x4*
      x7*Z^5+43*x1*x2^2*x3*x6*x7*Z^5-24*x1*x4^2*x5*x6*Z^6+3*x4^2*x5^2*x6*Z^6+48*x1*x2*x5*x6^2*Z^6-6*x2*x5^2*x6^2*Z^6+10*x1*x2^2*
      x6*x7*Z^6+6*x1*x2*x6^2*x7*Z^6,-x1^3*x4+x1^2*x2*x5,2*x1*x2*x4^2-2*x2^2*x4*x5-x1*x2^2*x6+x2^3*x7,-2*x3^3*x5^2*x7^2-x1*x3^3*
      x7^3-6*x3^2*x5*x7^3*Z-16*x1*x5^2*x6*x7*Z^2-16*x2*x5^2*x7^2*Z^2-8*x1*x2*x7^3*Z^2-3*x3*x7^4*Z^2+8*x7^4*Z^3,-2*x4^4+2*x2*x4^2
      *x6,-27*x1*x2^3*x3^5*x5-29*x1*x2^3*x3^4*x5*Z-36*x1*x2^2*x3^4*x4*x5*Z-27*x2^3*x3^4*x5^2*Z+43*x1*x2^2*x3^3*x4*x5*Z^2-9*x1*x2
      *x3^3*x4^2*x5*Z^2+47*x2^2*x3^3*x4*x5^2*Z^2-9*x1*x2^2*x3^3*x5*x6*Z^2+18*x2^3*x3^3*x5*x7*Z^2+10*x1*x2^2*x3^2*x4*x5*Z^3+24*x1
      *x2*x3^2*x4^2*x5*Z^3-10*x2^3*x3^2*x5^2*Z^3+38*x2^2*x3^2*x4*x5^2*Z^3-15*x2*x3^2*x4^2*x5^2*Z^3+24*x1*x2^2*x3^2*x5*x6*Z^3-3*
      x1*x2*x3^2*x4*x5*x6*Z^3-18*x2^2*x3^2*x5^2*x6*Z^3+10*x2^3*x3^2*x5*x7*Z^3+6*x2^2*x3^2*x4*x5*x7*Z^3+20*x2^2*x3*x4*x5^2*Z^4+48
      *x2*x3*x4^2*x5^2*Z^4+48*x2^2*x3*x5^2*x6*Z^4-6*x2*x3*x4*x5^2*x6*Z^4-20*x2^3*x3*x5*x7*Z^4-48*x2^2*x3*x4*x5*x7*Z^4+9*x2*x3*x4
      ^2*x5*x7*Z^4-18*x2^2*x3*x5*x6*x7*Z^4-24*x2*x4^2*x5*x7*Z^5+3*x4^3*x5*x7*Z^5+48*x2^2*x5*x6*x7*Z^5-6*x2*x4*x5*x6*x7*Z^5,-3*x1
      ^2*x2*x3^5*x4*x5-6*x1*x2^2*x3^5*x5^2-12*x1*x2*x3^4*x4*x5^2*Z-9*x2^2*x3^4*x5^3*Z-12*x1^2*x2*x3^4*x4*x7*Z-12*x1*x2^2*x3^4*x5
      *x7*Z-24*x1^2*x2^2*x3^2*x4*x5*Z^2-48*x1*x2^3*x3^2*x5^2*Z^2-15*x1^2*x3^3*x4^2*x7*Z^2-48*x1*x2*x3^3*x4*x5*x7*Z^2-27*x2^2*x3^
      3*x5^2*x7*Z^2+48*x1*x2^2*x3*x4*x5^2*Z^3+5*x1^2*x2^2*x3*x4*x7*Z^3+24*x1^2*x3^2*x4^2*x7*Z^3+5*x1*x2^3*x3*x5*x7*Z^3+24*x1*x2*
      x3^2*x4*x5*x7*Z^3-36*x1*x3^2*x4^2*x5*x7*Z^3+24*x2^2*x3^2*x5^2*x7*Z^3-12*x2*x3^2*x4*x5^2*x7*Z^3-18*x1*x2*x3^2*x4*x7^2*Z^3-
      18*x2^2*x3^2*x5*x7^2*Z^3-48*x1^2*x2*x4^2*x7*Z^4-24*x1*x2^2*x4*x5*x7*Z^4+48*x1*x3*x4^2*x5*x7*Z^4+48*x1*x2*x3*x4*x7^2*Z^4-18
      *x1*x3*x4^2*x7^2*Z^4+48*x2^2*x3*x5*x7^2*Z^4-15*x2*x3*x4*x5*x7^2*Z^4+48*x1*x4^2*x7^2*Z^5+24*x2*x4*x5*x7^2*Z^5-3*x4^2*x5*x7^
      2*Z^5,0,9*x1^3*x2^2*x3^7+9*x1^3*x2*x3^6*x4*Z+36*x1^2*x2^2*x3^6*x5*Z-29*x1^3*x2^3*x3^4*Z^2-24*x1^3*x2*x3^5*x4*Z^2+24*x1^2*
      x2^2*x3^5*x5*Z^2+39*x1^2*x2*x3^5*x4*x5*Z^2+30*x1*x2^2*x3^5*x5^2*Z^2+3*x1^3*x2*x3^5*x6*Z^2+18*x1^2*x2^2*x3^5*x7*Z^2-29*x1^3
      *x2^2*x3^3*x4*Z^3-29*x1^2*x2^3*x3^3*x5*Z^3-19*x1^2*x2*x3^4*x4*x5*Z^3-29*x1*x2^2*x3^4*x5^2*Z^3+45*x1*x2*x3^4*x4*x5^2*Z^3+15
      *x1^2*x2*x3^4*x5*x6*Z^3-24*x1^2*x2^2*x3^4*x7*Z^3+24*x1^2*x2*x3^4*x4*x7*Z^3+6*x1*x2^2*x3^4*x5*x7*Z^3+10*x1^3*x2^2*x3^2*x4*Z
      ^4-10*x1^2*x2^3*x3^2*x5*Z^4-5*x1^2*x2^2*x3^2*x4*x5*Z^4+24*x1*x2^3*x3^2*x5^2*Z^4-43*x1*x2*x3^3*x4*x5^2*Z^4+24*x1^3*x2^2*x3^
      2*x6*Z^4+18*x1*x2*x3^3*x5^2*x6*Z^4+29*x1^2*x2^3*x3^2*x7*Z^4-43*x1^2*x2*x3^3*x4*x7*Z^4-6*x1^2*x3^3*x4^2*x7*Z^4+43*x1*x2^2*
      x3^3*x5*x7*Z^4+48*x1*x2*x3^3*x4*x5*x7*Z^4+12*x1^2*x2*x3^3*x6*x7*Z^4-27*x1*x2^2*x3^3*x7^2*Z^4+20*x1^2*x2^2*x3*x4*x5*Z^5+48*
      x1^2*x2^2*x3*x5*x6*Z^5-20*x1^2*x2^3*x3*x7*Z^5+5*x1^2*x2^2*x3*x4*x7*Z^5-10*x1^2*x2*x3^2*x4*x7*Z^5+48*x1*x2^3*x3*x5*x7*Z^5+
      10*x1*x2^2*x3^2*x5*x7*Z^5+39*x1*x2*x3^2*x4*x5*x7*Z^5-9*x1*x3^2*x4^2*x5*x7*Z^5+15*x2*x3^2*x4*x5^2*x7*Z^5-24*x1^2*x2*x3^2*x6
      *x7*Z^5+3*x1^2*x3^2*x4*x6*x7*Z^5+27*x1*x2*x3^2*x5*x6*x7*Z^5+14*x1*x2^2*x3^2*x7^2*Z^5-27*x1*x2*x3^2*x4*x7^2*Z^5-48*x1^2*x2*
      x4^2*x7*Z^6+24*x1*x2^2*x4*x5*x7*Z^6-20*x1*x2*x3*x4*x5*x7*Z^6-48*x2*x3*x4*x5^2*x7*Z^6+24*x1^2*x2^2*x6*x7*Z^6-48*x1*x2*x3*x5
      *x6*x7*Z^6+6*x1*x3*x4*x5*x6*x7*Z^6+20*x1*x2^2*x3*x7^2*Z^6-5*x1*x2*x3*x4*x7^2*Z^6-18*x1*x3*x4^2*x7^2*Z^6+3*x2*x3*x4*x5*x7^2
      *Z^6+9*x1*x2*x3*x6*x7^2*Z^6+48*x1*x4^2*x7^2*Z^7-24*x2*x4*x5*x7^2*Z^7-3*x4^2*x5*x7^2*Z^7-24*x1*x2*x6*x7^2*Z^7+3*x1*x4*x6*x7
      ^2*Z^7,3*x1*x3^5*x4*x5^2+3*x1*x2*x3^5*x5*x7+8*x1^2*x2*x3^3*x4*x5*Z+9*x1*x3^4*x5^2*x6*Z+9*x1*x2*x3^4*x7^2*Z+48*x1*x2*x3^2*
      x4*x5^2*Z^2+24*x1^2*x2*x3^2*x5*x6*Z^2+24*x1^2*x2*x3^2*x4*x7*Z^2+24*x1*x2^2*x3^2*x5*x7*Z^2+x3^3*x4*x5^2*x7*Z^2+9*x1*x3^3*x5
      *x6*x7*Z^2+9*x1*x3^3*x4*x7^2*Z^2+x2*x3^3*x5*x7^2*Z^2-37*x1^2*x2^2*x4*x5*Z^3+48*x1^2*x3*x4*x5*x6*Z^3+24*x1^2*x3*x4^2*x7*Z^3
      -24*x1*x3^2*x5*x6*x7*Z^3+3*x3^2*x5^2*x6*x7*Z^3-24*x1*x3^2*x4*x7^2*Z^3+6*x1*x3^2*x6*x7^2*Z^3+3*x2*x3^2*x7^3*Z^3-27*x1^2*x4*
      x5*x6*Z^4+16*x1^2*x5*x6^2*Z^4+37*x1^2*x4^2*x7*Z^4+16*x2*x4*x5^2*x7*Z^4+16*x1^2*x4*x6*x7*Z^4+8*x2^2*x5*x7^2*Z^4+3*x3*x5*x6*
      x7^2*Z^4+3*x3*x4*x7^3*Z^4-8*x5*x6*x7^2*Z^5-8*x4*x7^3*Z^5+2*x6*x7^3*Z^5,-2*x5^4+2*x1*x5^2*x7,-2*x1*x2^3*x3^3-3*x1*x2^2*x3^2
      *x4*Z-24*x1*x2^4*Z^2+x1*x2*x4*x6*Z^3,-x2^2*x4*x5+x1*x2^2*x6,6*x1*x2^3*x3^7+8*x1*x2^3*x3^6*Z+8*x1*x2^2*x3^6*x4*Z+24*x1*x2^4
      *x3^4*Z^2-24*x1*x2^2*x3^5*x4*Z^2-18*x2^3*x3^5*x7*Z^2+27*x1*x2^4*x3^3*Z^3-45*x1*x2^3*x3^3*x4*Z^3+48*x1*x2^2*x3^4*x6*Z^3+24*
      x2^3*x3^4*x7*Z^3-30*x2^2*x3^4*x4*x7*Z^3+10*x1*x2^5*x3*Z^4+10*x1*x2^3*x3^2*x4*Z^4+37*x1*x2^2*x3^3*x6*Z^4+2*x1*x2*x3^3*x6^2*

### 2021-04-20 FastLinAlg/M2/ChangesMade_ResponseToReviewers.txt

      Z^4-29*x2^4*x3^2*x7*Z^4-37*x2^3*x3^3*x7*Z^4+27*x2^2*x3^3*x4*x7*Z^4-8*x2*x3^3*x4^2*x7*Z^4+7*x1*x2^5*Z^5+37*x1*x2^4*x4*Z^5-
      20*x1*x2^3*x3*x6*Z^5+20*x2^4*x3*x7*Z^5+48*x2^3*x3*x4*x7*Z^5+10*x2^2*x3^2*x4*x7*Z^5+24*x2*x3^2*x4^2*x7*Z^5-43*x2^2*x3^2*x6*
      x7*Z^5-7*x1*x2^3*x6*Z^6+16*x1*x2^2*x6^2*Z^6+7*x2^4*x7*Z^6-27*x2^3*x4*x7*Z^6+8*x2^2*x4^2*x7*Z^6-30*x2^2*x3*x6*x7*Z^6-48*x2*
      x3*x4*x6*x7*Z^6-6*x2*x3*x6^2*x7*Z^6-7*x2^2*x6*x7*Z^7-37*x2*x4*x6*x7*Z^7+16*x2*x6^2*x7*Z^7-2*x4*x6^2*x7*Z^7,-2*x1*x2*x3^6*
      x5*x7-3*x2*x3^5*x5^2*x7*Z-48*x1*x2^2*x3^3*x5*x7*Z^2-3*x1*x3^4*x5*x6*x7*Z^2-3*x2*x3^4*x5*x7^2*Z^2-48*x2^2*x3^2*x5^2*x7*Z^3+
      24*x1^2*x2*x3^2*x6*x7*Z^3+8*x1*x3^3*x5*x6*x7*Z^3-x3^3*x5^2*x6*x7*Z^3+8*x2*x3^3*x5*x7^2*Z^3-7*x1*x3^3*x6*x7^2*Z^3+47*x1*x2^
      3*x5*x7*Z^4-48*x1*x2*x3*x5*x6*x7*Z^4-48*x2^2*x3*x5*x7^2*Z^4+24*x1*x3^2*x6*x7^2*Z^4+27*x1*x2*x5*x6*x7*Z^5-16*x2*x5^2*x6*x7*
      Z^5+8*x1^2*x6^2*x7*Z^5+27*x2^2*x5*x7^2*Z^5+16*x1*x2*x6*x7^2*Z^5+3*x3*x6*x7^3*Z^5-8*x6*x7^3*Z^6,-3*x1^2*x2^2*x3^2*x7-6*x1*
      x2^2*x3*x5*x7*Z-3*x1*x2^2*x7^2*Z^2,-6*x1*x2^2*x3^5*x5^2-6*x1*x2*x3^4*x4*x5^2*Z-6*x2^2*x3^4*x5^3*Z-18*x1*x2^2*x3^4*x5*x7*Z-
      48*x1*x2^3*x3^2*x5^2*Z^2-12*x1*x2*x3^3*x5^2*x6*Z^2-30*x2^2*x3^3*x5^2*x7*Z^2-10*x1*x2^2*x3*x4*x5^2*Z^3+15*x2^3*x3*x5^3*Z^3+
      48*x1*x2*x3^2*x5^2*x6*Z^3-18*x2*x3^2*x5^3*x6*Z^3-48*x2^2*x3^2*x5^2*x7*Z^3+18*x2*x3^2*x4*x5^2*x7*Z^3-6*x1*x2*x3^2*x5*x6*x7*
      Z^3-12*x2^2*x3^2*x5*x7^2*Z^3-5*x1*x2^2*x5^2*x6*Z^4-5*x2*x3*x5^3*x6*Z^4-43*x2^3*x5^2*x7*Z^4+5*x2*x3*x4*x5^2*x7*Z^4-12*x2*x3
      *x5^2*x6*x7*Z^4+12*x2*x3*x4*x5*x7^2*Z^4);

i55 :  time randomPoints(J2, Strategy=>MultiplicationTable)
RandomRationalPoints.m2:840:17:(3):[12]: error: expected a polynomial ring
RandomRationalPoints.m2:840:17:(3):[12]: --entering debugger (type help to see debugger commands)                                
RandomRationalPoints.m2:840:17-840:79: --source code:                                                                            
            m0:=contract(transpose matrix entries b2,matrix entries((xx_0*b1)%Js));

i56 : time randomPoints(J2, Strategy=>Default)
     -- used 4.2498 seconds

o56 = {{0, 0, 23, 0, 0, 42, 29, 0}}

o56 : List

### 2021-04-20 FastLinAlg/Paper/RandomRationalPoints.tex
Various changes on the paper, and on the main code.

    When working over very small fields, frequently {\tt BruteForce} is most efficient.  This is not surprising as there may not be many points to check, and a surprisingly large percentage of points can be rational in hypersurfaces and complete intersections.  However, if the field size is larger, {\tt BruteForce} will perform poorly.  Even for some simple examples, it could not provide any rational points if the number of trials is not enough. Other strategies work differently on different examples, and even the same strategy can sometimes work very quickly even if it typically works very slowly. Providing {\tt codimension} speeds up computations significantly as computing codimension using the default command {\tt codim} creates a bottleneck. If codimension needs to be computed, we  circumvent this issue using a probabilistic code to compute it (see \Cref{helper}). A quick comment, while in many examples generic projection works well, there are some examples where it is many orders of magnitude slower.  By default, generic projection is turned off in the default strategy, that is we set {\tt ProjectionAttempts=>0}.  Increasing this number will include it.

>>>>

    When working over very small fields, frequently {\tt BruteForce} is most efficient.  This is not surprising as there may not be many points to check.  However, if the field size is larger, {\tt BruteForce} will perform poorly.  Even for some simple examples, it could not provide any rational points if the number of trials is not enough.  Other strategies work differently on different examples, and the same strategy can sometimes work very quickly even if it typically works very slowly.

    Providing {\tt codimension} speeds up computations significantly as computing codimension using the default command {\tt codim} creates a bottleneck in some cases. If codimension needs to be computed, we  circumvent this issue using a probabilistic code to compute it (see \Cref{helper}). A quick comment, while in many examples generic projection works well, there are some examples where it is many orders of magnitude slower.  By default, generic projection is turned off in the default strategy, that is we set {\tt ProjectionAttempts=>0}.  See \autoref{rem.ProjectingToAHypersurfaceFirst} for additional related discussion.
